% Created by Husain Alshehhi
% 01302014
% Homework template

\documentclass[10pt]{article}
\usepackage{geometry}
\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{setspace}
\usepackage{enumerate}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{fancyhdr}
\usepackage{listings}
\usepackage{algorithm2e}
\usepackage[usenames,dvipsnames]{color}
\usepackage[utf8]{inputenc}
\usepackage{pdfpages}
\usepackage{url}
%\usepackage{pslatex}
%\usepackage{inconsolata}

% Global variables
\newcommand{\name}{Husain Alshehhi}
\newcommand{\course}{CSCE 411}
\newcommand{\homeworkNumber}{Report}
\newcommand{\duedate}{February 19, 2014}
\newcommand{\horrule}[1]{\rule{\linewidth}{#1}}

% Theorem environments
\theoremstyle{plain}
\newtheorem*{theorem*}{Theorem}
\newtheorem{theorem}{Theorem}
\newtheorem*{lemma*}{Lemma}
\newtheorem{lemma}{Lemma}
\newtheorem*{proposition*}{Proposition}
\newtheorem{proposition}{Proposition}
\newtheorem*{corollary*}{Corollary}
\newtheorem{corollary}{Corollary}

\theoremstyle{definition}
\newtheorem*{remark*}{Remark}
\newtheorem{remark}{Remark}
\newtheorem*{definition*}{Definition}
\newtheorem{definition}{Definition}
\newtheorem*{solution*}{Solution}
\newtheorem{solution}{Solution}
\newtheorem*{exercise*}{Exercise}
\newtheorem{exercise}{Exercise}
\newtheorem*{problem*}{Problem}
\newtheorem{problem}{Problem}

% The style of the page
\geometry{letterpaper}
\onehalfspacing
%doublespacing
\pagestyle{fancy}
\lhead{\name \hfill \homeworkNumber}

\newcommand{\N}{\mathbb N}
\newcommand{\Z}{\mathbb Z}
\newcommand{\Q}{\mathbb Q}
\newcommand{\R}{\mathbb R}
\newcommand{\C}{\mathbb C}
\newcommand{\Zp}{\mathbb Z^+}
\newcommand{\Qp}{\mathbb Q^+}
\newcommand{\Rp}{\mathbb R^+}

\newcommand{\set}[1]{\{ #1 \}}
\newcommand{\floor}[1]{\left\lfloor #1 \right\rfloor}
\newcommand{\ceil}[1]{\left\lceil #1 \right\rceil}
\newcommand{\abs}[1]{\left| #1 \right|}
\newcommand{\brac}[1]{\left( #1 \right)}
\newcommand{\vect}[1]{\left\langle #1 \right\rangle}

\lstset{
  basicstyle=\footnotesize\ttfamily,	
  breakatwhitespace=false,         		
  breaklines=true,                 		
  captionpos=b,
  escapeinside={\%*}{*)},          		
  extendedchars=true,
  frame=single,
  keepspaces=true,                 	
  language=C,                 		
  numbers=none,                    		
  %numbersep=5pt,                   		
  showspaces=false,                		
  showstringspaces=false,          		
  showtabs=false,                  		
  stepnumber=2,                    		
  tabsize=4,
  caption=\texttt{\lstname},
  title=\texttt{\lstname}
}

% Title
\title{
	\horrule{0.5pt}\\
	\Large \course: \homeworkNumber\\
    \normalsize \name \\
    \normalsize \duedate \\
    \horrule{0.5pt}\\
}
\author{}
\date{}

\begin{document}
\maketitle

In \texttt{frame\_pool.C}, I tried to implement the \texttt{frame\_pool} class. First, I tried to keep track of the frames I have within that space in memory I have. If I am given 0 as an input for \texttt{\_info\_frame\_no}, I consider the starting frame. Then I clear all the frames.

In \texttt{get\_frame}, I wasn't sure what to do. I am confident that I should look for a non-zero frame, but given that, I do not know what to return. I found some advice online, but it was non-understandable.

In \texttt{page\_table.C}, I implemented \texttt{enable\_paging} and \texttt{load} fine, according to the website. But I am not sure how to implement the rest. I looked online for help and read several manuals, but still the implementation we use in class is very different that anything I read.

\end{document}
